---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<br>

##_pkgdown website for the ohicore is currently under development_

# ohicore

The `ohicore` is a package of core functions for calculating the Ocean Health Index. The goal of ohicore is to ... For more, please visit [OHI-Science.org](http://ohi-science.org).
See [ohi-science.org/toolbox-training](http://ohi-science.org/toolbox-training) for more information on using the `ohicore` for ocean health assessments.


## Installation

You can install ohicore from github with:

```{r gh-installation, eval = FALSE}
# devtools is needed for installing packages from Github
# install.packages("devtools")

# install packages
devtools::install_github('ohi-science/ohicore')
library(ohicore)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```