---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# OHICORE

The `ohicore` is a package of core functions for calculating the Ocean Health Index (OHI). The goal of ohicore is to facilitate calculation of OHI scores both for the annual global assessments and regional assessments, within a [tailorable framework](https://peerj.com/articles/1503/). For more information, please visit [OHI-Science.org](http://ohi-science.org). See [ohi-science.org/toolbox-training](http://ohi-science.org/toolbox-training) for more on using the `ohicore` for ocean health assessments.


## Installation

You can install ohicore from github with:

```{r gh-installation, eval = FALSE}
# devtools is needed for installing packages from Github
# install.packages("devtools")

# install packages
devtools::install_github('ohi-science/ohicore')
library(ohicore)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

### Preview pkgdown Website

```{r preview pkgdown site}
library(pkgdown)
preview_site()
```