---
title: "Updating name 2 region synonyms"
output: html_document
date: "2023-08-07"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script can be used to update the synonyms in name_2_rgn as well as confirm that the update was successful.

**1.)** Run the code below to update the synonyms list in name_2 region. If you need to delete or edit existing synonyms open \~/data_raw/rgn_eez_v2013a_synonyms.csv and manually edit the file.

```{r v2023-updates, eval=FALSE}
library(tidyverse)
load(here::here("data/rgn_master.rda"))

#new synonyms, update with NEW synonyms
new_synonyms <- c("China, Macao Special Administrative Region",
                  "China, Hong Kong Special Administrative Region")

#region ids, update with the matching region id for the synonym
#put NA for landlocked or disputed
region_ids <- c(209, 209) 

#rgn type (must be be ohi_region, landlocked, or disputed)
region_types <- c("ohi_region", "ohi_region")

#run the function to add synonyms 
source(here::here("updating_functions/name_2_rgn/update_synonyms.R"))


# Check output, if duplicate names are found they aren't added so will ask you to confirm that the ohi region names are correct and then tell you whether there were duplicates identified or not 
update_synonyms(synonyms_list = new_synonyms,
                region_id_list = region_ids,
                rgn_type_list = region_types)
```

**2)** Rerun data_prepare.R to update the rda files stored in the data folder

```{r}
source(here::here("data_raw/data_prepare.R"))
```

**3)** Confirm that the update was successful

-   If you experience unexpected issues when testing the update, you may need to update the name_2_rgn function stored in the R folder.

```{r}
#source the functions for testing the synonyms 
source(here::here("updating_functions/name_2_rgn/test_synonyms.R"))

#source the latest version of name_2_rgn
source(here::here("R/name_2_rgn.R"))

#run the test_synonyms function
#to add the synonyms to the test data frame set append_synonyms to true, do not do this until you have confirmed they are working as expected

#review output, confirm your synonyms were not removed for not having any match in the lookup tables 
#review the results data frame and check that the synoynms you added were assigned to the correct region. 


results <- test_synonyms(new_synonyms)
```

**4)** Push changes to the ohicore repository. Reinstall ohicore from the dev branch to use the updated function.
