---
title: "Updating name 2 region synonyms"
output: html_document
date: "2023-08-07"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script can be used to update the synonyms in name_2_rgn as well as confirm that the update was successful.

**1.)** Run the code below to update the synonyms list in name_2 region. If you need to delete or edit existing synonyms open \~/data_raw/rgn_eez_v2013a_synonyms.csv and manually edit the file.

```{r}
library(tidyverse)
load(here::here("data/rgn_master.rda"))

#new synonyms, update with new synonyms
new_synonyms <- c("congo - brazzaville",
                  "congo - kinshasa",
                  "myanmar (burma)",
                  "st. vincent and grenadines",
                  "u.s. virgin islands")

#region ids, update with the matching region id for the synonym
#put NA for landlocked or disputed
region_ids <- c(100,199, 205, 127, 116) 

#rgn type (must be be ohi_region, landlocked, or disputed)
region_types <- c("ohi_region", "ohi_region", "ohi_region", "ohi_region", "ohi_region")

#run the function to add synonyms 
source(here::here("updating_functions/name_2_rgn/update_synonyms.R"))

update_synonyms(new_synonyms, region_ids, region_types)
```

**2)** Rerun data_prepare.R to update the rda files stored in the data folder

```{r}
source(here::here("data_raw/data_prepare.R"))
```

**3)** Confirm that the update was successful

-   If you experience unexpected issues when testing the update, you may need to update the name_2_rgn function stored in the R folder.

```{r}
#source the functions for testing the synonyms 
source(here::here("updating_functions/name_2_rgn/test_synonyms.R"))

#source the latest version of name_2_rgn
source(here::here("R/name_2_rgn.R"))

#run the test_synonyms function
#to add the synonyms to the test data frame set append_synonyms to true, do not do this until you have confirmed they are working as expected

#review output, confirm your synonyms were not removed for not having any match in the lookup tables 
#review the results data frame and check that the synoynms you added were assigned to the correct region. 


results <- test_synonyms(new_synonyms)
```

**4)** Push changes to the ohicore repository. Reinstall ohicore from the dev branch to use the updated function.
