---
output: html_document
---

```{r set up, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(tidyverse)

## information from layers.csv
key <- "toolbox-demo"
dir_scenario_gh <- "https://raw.githubusercontent.com/OHI-Science/toolbox-demo/master/region2016"
layers_csv  <- readr::read_csv(file.path(dir_scenario_gh, 'layers.csv'))
layers_web <- sprintf('http://ohi-science.org/%s/layers.html', key)
```


## Food Provision: Fisheries

```{r, child='goals/FIS.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="FIS") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Food Provision: Mariculture

```{r, child='goals/MAR.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="MAR") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Artisanal Fishing Opportunity 

```{r, child='goals/AO.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="AO") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Natural Products

```{r, child='goals/NP.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="NP") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Carbon Storage

```{r, child='goals/CS.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="CS") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Coastal Protection

```{r, child='goals/CP.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="CP") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Tourism & Recreation

```{r, child='goals/TR.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="TR") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Livelihoods & Economies: Livelihoods

```{r, child='goals/LIV.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="LIV") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```


---- 

## Livelihoods & Economies: Economies

```{r, child='goals/ECO.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="ECO") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Sense of Place: Iconic Species

```{r, child='goals/ICO.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="ICO") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Sense of Place: Lasting Special Places

```{r, child='goals/LSP.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="LSP") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Clean Waters

```{r, child='goals/CW.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="CW") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Biodiversity: Species

```{r, child='goals/SPP.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="SPP") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Biodiversity: Habitats

```{r, child='goals/HAB.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="HAB") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

